---
title: "R Notebook"
output: html_notebook
---

## Congruential Random Number Generator

Write R code to generate $N = 1000$ pseudo-random numbers using a congruential random number generator.
Choose reasonable values for the multiplier, increment, and modulo. Use your student ID as a seed.




## Inversion sampler for the Pareto distribution

(a) inverse CDF of the Pareto distribution is

$$
F^{-1}(u) = \frac{a}{(1-u)^{\frac{1}{b}}}\quad 0\leq u < 1
$$
(b) Write R code for an inversion sampler to generate a sample of $N = 1000$ random numbers from the Pareto distribution with $a = 2$ and $b = 3$. Use the generated CNRG pseudo-random numbers of Question 1.


(c) Draw a histogram for the generated sample and add a line with the true density of the `Pareto(2, 3)` distribution.

```{r}
hist(x)
```

## Inversion sampler for a discrete random variable

(a) Write R code for an inversion sampler to generate a sample of 1000 random numbers from the distribution of X


(b) Show the probability mass function of the sample of simulated random numbers. Include the true probability mass function in the plot for a comparison.

```{r}
barplot(rbind(table(x) / m, mass), beside=TRUE)
```

## Inversion sampler for the binomial distribution

(a) Write R code for an inversion sampler to generate a sample of 1000 random numbers from a binomial distribution with $n = 12$ Bernoulli trials and the probability of success on each trial of $p = 0.8$.




(b) Show the probability mass function of the sample of simulated binomial random numbers. Include the true binomial probability mass function in the plot for a comparison.

```{r}
barplot(rbind(smass/m, mass), beside=TRUE)
```

## Rolling dice

(a) Generate a sample of $N = 1000$ totals of rolling the three dice, using an inversion sampler




(b) Show the probability mass function of the sample of simulated totals.

```{r}
barplot(smass/N)
```

















